---
title: "L System Fractals in R using R6 classes - Examples, Koch Curves"
output: html_document
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'examples_3.html'))})
---
```{r}
source("fractal_l.R")
```


```{r include=FALSE}
row_num <- 11
max_generation <- 12
```
# Koch Curve
##### Generation n = `r (max_generation)`
##### Angle = `r (l_systems$l_angles[row_num])`
##### Initiator = `r (l_systems$l_initiators[row_num])`
##### Generator(s) = `r (l_systems$l_F_generators[row_num])`
##### `r (l_systems$l_f_generators[row_num])`
##### `r (l_systems$l_names[row_num])`
```{r echo=FALSE}
plot_fractal_l(l_systems_row_num=row_num,l_systems_max_generation=max_generation)
```


```{r include=FALSE}
row_num <- 12
max_generation <- 6
```
# Koch Curve
##### Generation n = `r (max_generation)`
##### Angle = `r (l_systems$l_angles[row_num])`
##### Initiator = `r (l_systems$l_initiators[row_num])`
##### Generator(s) = `r (l_systems$l_F_generators[row_num])`
##### `r (l_systems$l_f_generators[row_num])`
##### `r (l_systems$l_names[row_num])`
```{r echo=FALSE}
plot_fractal_l(l_systems_row_num=row_num,l_systems_max_generation=max_generation)
```


```{r include=FALSE}
row_num <- 13
max_generation <- 4
```
# Hexagonal Gosper curve
##### Generation n = `r (max_generation)`
##### Angle = `r (l_systems$l_angles[row_num])`
##### Initiator = `r (l_systems$l_initiators[row_num])`
##### Generator(s) = `r (l_systems$l_F_generators[row_num])`
##### `r (l_systems$l_f_generators[row_num])`
##### `r (l_systems$l_names[row_num])`
```{r echo=FALSE}
plot_fractal_l(l_systems_row_num=row_num,l_systems_max_generation=max_generation)
```


```{r include=FALSE}
row_num <- 14
max_generation <- 3
```
# Quadratic Gosper curve
##### Generation n = `r (max_generation)`
##### Angle = `r (l_systems$l_angles[row_num])`
##### Initiator = `r (l_systems$l_initiators[row_num])`
##### Generator(s) = `r (l_systems$l_F_generators[row_num])`
##### `r (l_systems$l_f_generators[row_num])`
##### `r (l_systems$l_names[row_num])`
```{r echo=FALSE}
plot_fractal_l(l_systems_row_num=row_num,l_systems_max_generation=max_generation)
```

