---
title: "L System Fractals in R using R6 classes - Examples."
output: html_document
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'examples_1.html'))})
---
```{r}
source("fractal_l.R")
```

```{r}

#plot_fractal_l(l_systems_row_num=5,l_systems_max_generation=3)
```
```{r}
#plot_fractal_l(l_systems_row_num=6,l_systems_max_generation=4)
```

```{r include=FALSE}
row_num <- 7
max_generation <- 4
```
# Koch Curve
##### Generation n = `r (max_generation)`
##### Angle = `r (l_systems$l_angles[row_num])`
##### Initiator = `r (l_systems$l_initiators[row_num])`
##### Generators = `r (l_systems$l_F_generators[row_num])`
##### `r (l_systems$l_names[row_num])`
 `r (l_systems$l_f_generators[row_num])`
```{r echo=FALSE}
plot_fractal_l(l_systems_row_num=row_num,l_systems_max_generation=max_generation)
```

```{r}
#plot_fractal_l(l_systems_row_num=8,l_systems_max_generation=4)
```

```{r}
#plot_fractal_l(l_systems_row_num=9,l_systems_max_generation=5)
```

```{r include=FALSE}
row_num <- 10
max_generation <- 4
```
# Koch Curve
##### Generation n = `r (max_generation)`
##### Angle = `r (l_systems$l_angles[row_num])`
##### Initiator = `r (l_systems$l_initiators[row_num])`
##### Generators = `r (l_systems$l_F_generators[row_num])`
##### `r (l_systems$l_names[row_num])`
 `r (l_systems$l_f_generators[row_num])`
```{r echo=FALSE}
plot_fractal_l(l_systems_row_num=row_num,l_systems_max_generation=max_generation)
```
