---
title: "L System Fractals in R using R6 classes."
output: html_document
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
---
By: Jeff Blackadar @jeffblackadar

## References
Prusinkiewicz, Przemyslaw, and Aristid Lindenmayer. The Algorithmic Beauty of Plants. New York u.a: Springer, 1990.

Spannbauer, Adam. OOP Fractal Trees in R with R6, ggplot2, & gganimate (part 1) https://adamspannbauer.github.io/2018/10/07/oop-fractal-trees-in-r-with-r6-ggplot2-gganimate-part-1/

Thanks to Adam Spannbauer's article noted above, R6 classes and plotting of fractals are used here. Page numbers referenced refer to Przemyslaw Prusinkiewicz and Aristid Lindenmayer's The Algorithmic Beauty of Plants.

Scroll down to see some examples, or view the other pages.  The repository for code used here is https://github.com/jeffblackadar/fractal.



```{r fractal_l.R classes, echo=TRUE, code = readLines("fractal_l.R")}

 
```


```{r include=FALSE}
row_num <- 15
max_generation <- 4
```
# Koch Snowflake
##### Generation n = `r (max_generation)`
##### Angle = `r (l_systems$l_angles[row_num])`
##### Initiator = `r (l_systems$l_initiators[row_num])`
##### Generators = `r (l_systems$l_F_generators[row_num])`
##### `r (l_systems$l_names[row_num])`
 `r (l_systems$l_f_generators[row_num])`
```{r echo=FALSE}
plot_fractal_l(l_systems_row_num=row_num,l_systems_max_generation=max_generation)
```



```{r include=FALSE}
row_num <- 16
max_generation <- 8
```
# Tree
##### Generation n = `r (max_generation)`
##### Angle = `r (l_systems$l_angles[row_num])`
##### Initiator = `r (l_systems$l_initiators[row_num])`
##### Generators = `r (l_systems$l_F_generators[row_num])`
##### `r (l_systems$l_names[row_num])`
 `r (l_systems$l_f_generators[row_num])`
```{r echo=FALSE}
plot_fractal_l(l_systems_row_num=row_num,l_systems_max_generation=max_generation)
```

